Compare scANVI and SingleR annotations

### 2025-08-14 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/scanvi-singler-comparison.Rmd
restore histogram and show ridge plot with vline

First, what is the distribution of posterior probabilities for assigned labels?
We'll look at the minimum, maximum, and median posterior probabilities across libraries in a table.

```{r}
scanvi_df |>
  tidyr::separate(cell_id, into = c("library_id", "barcode"), remove = FALSE) |>
  dplyr::group_by(library_id) |>
  dplyr::summarize(
    library_size = dplyr::n(), 
    min_posterior = min(scanvi_posterior), 
    median_posterior = median(scanvi_posterior), 
    max_posterior = max(scanvi_posterior)
  ) |>
  dplyr::arrange(library_size)
```

Across libraries, the median posterior probability is always exceptionally high at >=0.99, which suggests `scANVI` confidence is roughly the same across libraries.

@@

```{r fig.height=8, fig.width=8}
scanvi_df |>
  dplyr::group_by(scanvi) |>
  dplyr::mutate(scanvi = glue::glue("{scanvi} (n={dplyr::n()})")) |>
  ########### into ggplot ############
  ggplot() + 
    aes(y = forcats::fct_infreq(scanvi), x = scanvi_posterior) + 
    # show the median
    ggridges::stat_density_ridges(quantile_lines = TRUE, quantiles = 2, alpha = 0.7) +
    labs(x = "posterior probability", y = "scANVI label (number of cells)") 
```

@@

A `0.75` threshold seems like it may be a good middle-ground for preserving labels while removing low-confidence annotations. 
What effect will this have?

@@

This will throw out a bit under 2% of cells:

>>>>

First, what is the distribution of posterior probabilities for assigned labels?
We'll make a histogram below using a very visible color to ensure the plot is legible, where each panel is a library, and libraries are ordered by size.

```{r fig.height=12, fig.width=15}
scanvi_df |>
  tidyr::separate(cell_id, into = c("library_id", "barcode"), remove = FALSE) |>
  dplyr::add_count(library_id) |>
  dplyr::mutate(
    library_id = glue::glue("{library_id} (N={n})"),
    library_id = factor(library_id), 
    library_id = forcats::fct_infreq(library_id), 
    library_id = forcats::fct_rev(library_id)
  ) |>
  ############ into ggplot ################
  ggplot() + 
  aes(x = scanvi_posterior) + 
  # ugly but _very visible_ color
  geom_histogram(bins = 100, fill = "magenta", color = "magenta") + 
  facet_wrap(vars(library_id), scales = "free_y", ncol = 7)
```

Across libraries, the median posterior probability is always exceptionally high at which suggests `scANVI` confidence is roughly the same across libraries.

@@

```{r fig.height=8, fig.width=8}
scanvi_ridgeplot <- scanvi_df |>
  dplyr::group_by(scanvi) |>
  dplyr::mutate(scanvi = glue::glue("{scanvi} (n={dplyr::n()})")) |>
  ########### into ggplot ############
  ggplot() + 
    aes(y = forcats::fct_infreq(scanvi), x = scanvi_posterior) + 
    # show the median
    ggridges::stat_density_ridges(quantile_lines = TRUE, quantiles = 2, alpha = 0.7) +
    labs(x = "posterior probability", y = "scANVI label (number of cells)") 
scanvi_ridgeplot
```

@@

A `0.75` threshold seems like it may be a good middle-ground for preserving labels while removing low-confidence annotations:

```{r fig.height=8, fig.width=8}
scanvi_ridgeplot +
  geom_vline(xintercept = 0.75, color = "firebrick")
```

How many cells will this remove?

@@

What are those cell types?
